Supplemental Materials, Methods and Results

### 2021-04-30 supp.Rmd
Cleaned supplement

## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)

PredatorAC <- lmer(dL ~ Predator + Population + BodyRegion +  
                           + Population:BodyRegion + (1|ID), data= Predator) # we have gularbot for Kenya but not Hawaii, so exclude it
anova(PredatorAC)
ranova(PredatorAC)

#for random effects, use ranova (is variance > 0?) report just LRT and df and need the SD of residuals and random effects from summary (just report random effects)

Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorAC2 <- lmer(dL ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorAC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0",
                                                    "Hawaii.midflank - Kenya.midflank = 0", 
                                                    "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))

# Chromatic Contast - dS

## Predator Model - Chromatic contrast (CC or dS)
## just this next section has Drew's code, which averages the backround (Leaf_B1, Leaf_B2, Leaf_T1, Leaf_T2, Stem1, Stem2) for each lizard body region measurement.
## This is the full model; however, we do not need background because the way the data is set up R is taking an average. See next model (background dropped)
PredatorCC <- lmer(sqrt_dS ~ Predator + Population + BodyRegion + Background 
                   + Predator:Background + Predator:BodyRegion + (1|ID), data=Predator)
Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorCC2 <- lmer(sqrt_dS ~ PopBRInt + (1|ID), data=Predator)
summary(glht(PredatorCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))

## dropping background from model (it is still averaged)
# anova gives us significance of fixed effects
# ranova tests random effects (note: report just LRT and df)
# need the SD of residuals and random effects from summary (just report random effects)

PredatorCC <- lmer(sqrt_dS ~ Predator + Population + BodyRegion +  
                     + Population:BodyRegion + (1|ID), data=Predator[Predator$BodyRegion!='gularbot',]) # we have gularbot for Kenya but not Hawaii, so exclude it
anova(PredatorCC)
ranova(PredatorCC)

### This is old code for when in the above model, predator was nonsignificant, so we can drop it from the model (below). But after sqrt it is significant, so don't use this code. Just keeping it in case.
PredatorCC <- lmer(sqrt_dS ~ Population + BodyRegion +  
                     + Population:BodyRegion + (1|ID), data=Predator[Predator$BodyRegion!='gularbot',]) # we have gularbot for Kenya but not Hawaii, so exclude it
anova(PredatorCC)
ranova(PredatorCC)
###

#for random effects, use ranova (is variance > 0?) report just LRT and df and need the SD of residuals and random effects from summary (just report random effects)

Predator$PopBRInt <- interaction(Predator$Population,Predator$BodyRegion)
PredatorCC2 <- lmer(sqrt_dS ~ PopBRInt + (1|ID), data=Predator[Predator$BodyRegion!='gularbot',])
summary(glht(PredatorCC2, linfct = mcp(PopBRInt = c("Hawaii.gular - Kenya.gular = 0","Hawaii.midflank - Kenya.midflank = 0", "Hawaii.topflank - Kenya.topflank = 0", 
                                                    "Hawaii.tailbase - Kenya.tailbase = 0" ))))

@@

#Making a point plot with error bars split by body size and population 
#Compute raw means and standard errors for body part and population for dS and assigned this data into Display_plot_dS_dat
Display_plot_dS_dat <- Display_1 %>% #data for dS Chromatic constrast
  group_by(Population, BodyRegion) %>% 
  summarise( Mean = mean(dS, na.rm = T), 
               SE = sd(dS)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

Display_plot_dL_dat <- Display_1 %>% #data for dL Achromatic contrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dL, na.rm = T), 
            SE = sd(dL)/sqrt(length(unique(ID))),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

>>>>

##########
## Chromatic Contrast - dL
########

  # Fit Model
        PredatorCC <- lmer(dS ~ Predator + Population + BodyRegion + Predator:BodyRegion + Predator:Population + (1|ID), data=Predator)
        summary(PredatorCC)
          anova(PredatorAC)

  # Robust variance estimators (RVE). Mostly all consistent
             Predator_subset <- Predator %>% filter(!is.na(Population), !is.na(BodyRegion))
           robust_PredatorCC <- coef_test(PredatorCC, cluster = Predator_subset$ID, vcov="CR2")

  # Fit model for linear hypothesis tests
    Predator$PopBRInt <- interaction(Predator$Population,Predator$Predator, Predator$BodyRegion)
          PredatorCC2 <- lmer(dS ~ -1 + PopBRInt + (1|ID), data=Predator)
          summary(PredatorCC2)

 # Contrasts hypothesis tests, but use RVE 
                 result6 <- Wald_test(PredatorCC2, constraints = constrain_pairwise(c(2:9), with_zero = TRUE), vcov="CR2", tidy = TRUE)
    result6$p_val_bonfer <- sapply(p.adjust(result6$p_val, "bonferroni"), function(x) p_value(x))

@@

#Making a point plot with error bars split by body size and population 
#Compute raw means and standard errors for body part and population for dS and assigned this data into Display_plot_dS_dat
Display_plot_dS_dat <- Display_1 %>% #data for dS Chromatic constrast
  group_by(Population, BodyRegion) %>% 
  summarise( Mean = mean(dS, na.rm = T), 
               SE = sd(dS)/sqrt(length(unique(ID))-1),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)

Display_plot_dL_dat <- Display_1 %>% #data for dL Achromatic contrast
  group_by(Population, BodyRegion) %>% 
  summarise(Mean = mean(dL, na.rm = T), 
            SE = sd(dL)/sqrt(length(unique(ID))-1),
            Upper = Mean + 1.96*SE,
            Lower = Mean - 1.96*SE)
